Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-09-29 sections/correlated-sicm-and-srfm.tex
Update correlated-sicm-and-srfm.tex

One of that techniques is STED microscopy (see section~\ref{sec:deterministic-approaches}). In a 
proof-of-principle study the topography of a group of fixed HeLa cells together with the 
distribution of actin filaments was investigated \cite{Hagemann2018}. Although both methods were 
able to investigate living cells, the cells needs to be fixed in that study, because the 
investigation was consecutively done onto two microscopes. The topography was measured with SICM 
and the distribution of actin with STED microscopy (see figure~\ref{fig:SICM_STED1}).

>>>>

% Hier füge ich jetzt einen Abschnitt zum diffraction limit ein. Ich habe gesehen das du (Patrick) 
% das in deiner SRFM-Einleitung nur im Kommentar eingefügt hattest.

The diffraction limit was defined by Ernst Abbe in 1873 \cite{Abbe1873} and could be described 
with the following equation.

\begin{equation}
d = \frac{\lambda}{2 n \sin{\alpha}}
\label{eq:Abbe_diff}
\end{equation}

In this equation $\lambda$ is the wavelength of light, $n$ the Brechungsindex (german) of the 
medium between objective and sample and $\alpha$ is half the opening Winkel (german) of the 
objective. Following this equation and under ideal conditions, the limit for structures, that 
could be resolved, would be halftimes the wavelength.

One of that techniques, that can resolve structures beyond the diffraction limit, is STED 
microscopy (see section~\ref{sec:deterministic-approaches}). In a proof-of-principle study the 
topography of a group of fixed HeLa cells together with the distribution of actin filaments was
investigated \cite{Hagemann2018}. Although both methods were able to investigate living cells, the 
cells were fixed in that study, because the investigation was done consecutively onto two 
microscopes. The topography was measured with SICM and the distribution of actin with STED 
microscopy (see figure~\ref{fig:SICM_STED1}).
